Adaptive Resolution Simulation in Equilibrium and Beyond

### 2014-11-12 writeDown/pub.epj/paper.tex
add abstract

%
\begin{document}
%
\title{Adaptive Resolution Simulation in Equilibrium and Beyond}
\author{Han Wang\inst{1,2}\fnmsep\thanks{\email{han.wang@fu-berlin.de}}, Animesh Agarwal\inst{3}}
%
\institute{CAEP Software Center for High Performance Numerical Simulation, Beijing, China
  \and Zuse Institute Berlin (ZIB), Germany
  \and Institut f\"ur Mathematik, Freie Universit\"at Berlin, Berlin, Germany}
%
\abstract{
Insert your abstract here.
} %end of abstract
%
\maketitle
%

>>>>

%
\begin{document}
%
\title{Adaptive Resolution Simulation in Equilibrium and Beyond}
\author{Han Wang\inst{1,2}\fnmsep\thanks{\email{han.wang@fu-berlin.de}}, Animesh Agarwal\inst{3}}
%
\institute{CAEP Software Center for High Performance Numerical Simulation, Beijing, China
  \and Zuse Institute Berlin (ZIB), Germany
  \and Institut f\"ur Mathematik, Freie Universit\"at Berlin, Berlin, Germany}
%
\abstract{ In this paper, we discuss the necessary conditions for
  accurate adaptive resolution simulation (AdResS) in equilibrium.
  The statistical and thermodynamical properties of two AdResS
  branches, i.e.~the force and the potential interpolations, are
  discussed and compared in parallel.  We further demonstrate the
  accuracy of AdResS in computing dynamical properties, which are not
  equilibrium ensemble averages, by the velocity auto-correlation of pure water
  and conformational relaxation of alanine dipeptide dissolved in water.
  Open questions are discussed in the end of the paper.
} %end of abstract
%
\maketitle
%
